An advanced control system such as a mobile robot may be required to perform many different tasks.
If the \envword\ set is finite, like selecting between ``map an environment'' and ``deliver a package'',
then its size is naturally quantified by the number of \envwords.
If the \envword\ set is infinite, like delivering packages with arbitrary mass and inertial properties,
then its size is not so easily quantified.
Even if the task space has a natural metric or measure,
these structures may be only weakly linked to the diversity of behavior
required for good performance on all \envwords.

In this work, we propose the 
\emph{$\alpha$-suboptimal covering number}
as a control-centric way to quantify infinite \envword\ spaces.
For a \envword\ space $\Envs$
and a suboptimality ratio $\alpha > 1$,
we define $\coveringnum{\alpha}{\Envs}$ as
the size of the smallest set of \singleenv\ policies $\coveringset$ %
such that for every $\env \in \Envs$, at least one ${\pi \in \coveringset}$
has a cost ratio no greater than $\alpha$ relative to the optimal policy for $\env$.
Similar notions of coverings appear in the literature on switching-based adaptive control,
but a key difference is our emphasis on suboptimality relative to the optimal policy for each task
rather than a single global performance measure (such as the $\cH_\infty$ norm).
We believe this captures the idea of a ``good multi-task policy''
in a way that is more meaningful for very diverse task sets,
where there is no reason to believe that the optimal costs for all tasks are similar.

We are also motivated by
\multienv\ paradigms in learning-based control, where the control policy is selected
from a parameterized family of functions
that map state and \envword\ parameters directly to actions.
As the \envword\ space grows, %
we expect to need a more expressive class of functions
to represent a good \multienv\ policy.
If the policies in a suboptimal cover $\coveringset$ are parameterized functions,
and a task can be efficiently mapped to its covering element(s),
then $\coveringset$ provides an upper bound on the number of parameters
needed to represent an $\alpha$-suboptimal \multienv\ policy.

To study suboptimal covering numbers in a concrete setting,
we consider linear dynamical systems with quadratic cost, or LQR problems.
We construct a family of well-behaved \multienv\ LQR problems 
where $\Envs$ is controlled by a ``breadth'' parameter $\breadth \in [1, \infty)$.
For the scalar special case,
we derive matching logarithmic upper and lower bounds on
$\coveringnum{\alpha}{\Envs_\breadth}$
with respect to $\breadth$.
As an effort towards analogous bounds for the matrix case,
we present experiments that attempt to shed light on the problem structure.
For the upper bound, we analyze properties of a logical extension of our scalar cover.
For the lower bound, we compare two natural choices of ``extremal''  \multienv\ LQR problems,
finding surprising topological behavior of the suboptimal neighborhoods for one option.

This paper is an initial step towards a comprehensive theory.






