A continuous-time, deterministic, infinite-horizon, time-invariant LQR problem with full-state feedback is defined by 
state space $\cX = \R^n$,
action space $\cU = \R^m$,
linear dynamics
\(
	\dot x = Ax + Bu,
\)
where $A \in \R^{n \times n},\ B \in \R^{n \times m}$, and quadratic cost 
\[
	J(\pi) = \E \left[
		\int_0^\infty 
			[x(t)^\top Q x(t) + u(t)^\top R u(t)] dt,
		\cond
		x(0) \sim \Normal(\zero, I),\ u(t) = \pi(x(t))
	\right],
\]
where $Q \succeq \zero$ and $R \succ \zero$ are cost matrices of appropriate dimensions
and $\Normal(\zero, I)$ is the unit Gaussian distribution.
For the purposes of this paper, the pair $(A, B)$ is \emph{controllable}
if $J(\pi) < \infty$ for some policy $\pi$.
If $(A, B)$ is controllable,
then the optimal policy %
is the linear
$u = \Kopt{} x$,
where $\Kopt{} \in \R^{m \times n}$
can be computed
by finding the unique maximal positive semidefinite solution $P$
of the algebraic Riccati equation
\(
	A^\top P + P A - P B R^{-1} B^\top P + Q = \zero
\)
(henceforth called the \emph{maximal solution})
and letting $\Kopt{} = -R^{-1} B^\top P$
\citep{kalman-contributions}.
Additionally, $J(\Kopt{}) = \trace{P}$.
An arbitrary controller $K \in \R^{m \times n}$ is \emph{stabilizing} if
$J(K) < \infty$,
in which case $J(K)$ satisfies
\begin{equation}
\label{eq:cost-suboptimal}
	J(K) = \trace{(Q + K^\top R K) W}\!, \
\text{where} \ \ 
	W = \int_0^\infty {e^{t(A + BK)}}^\top {e^{t(A + BK)}} dt.
\end{equation}
$W$ can be computed by solving the Lyapunov equation
\(
	(A + BK)^\top W + W (A + BK)  + I = \zero.
\)





\paragraph{\Multidyn\ LQR}
\label{sec:multilqr}
The most general formulation of \multienv\ LQR
would allow variations in each of $(A, B, Q, R)$,
but there is redundancy in this parameterization.
In particular, any LQR problem
where $Q \succ 0$
is equivalent via change of coordinates
to another LQR problem where $Q = I$ and $R = I$.
Therefore,
we consider only \emph{\multidyn} LQR problems where $Q = I_{n \times n}$ and $R = I_{m \times m}$
in this work.
Our reference policy class is linear: $\Refpolicies = \R^{m \times n}$.

A \multidyn\ LQR problem is defined by
$\Envs = \Aset \times \Bset$,
where $\Aset \subseteq \R^{n \times n}$ and ${\Bset \subseteq \R^{n \times m}}$.
It is not immediately clear how to design $\Aset$ and $\Bset$.
To support a rich analysis of suboptimal covers,
$\Envs$ should have a real-valued ``breadth'' parameter $\breadth$
that sweeps from a single \envword\ to sets with arbitrarily large, but finite, covering numbers.
A reasonable guess might be matrix norm balls of radius $\breadth$ with uncontrollable pairs removed,
but this can lead to an infinite covering number:
in the scalar problem defined by $\cA = \{a\},\ \Bset = [-\breadth, 0) \cup (0, \breadth]$, where $a > 0$,
it can be shown that
no $\alpha$-suboptimal cover is finite,
and no $\alpha$-suboptimal policy is continuous.


These properties are worrying, but the example $\cB$ is pathological.
The zero crossing is analogous to reversing the direction of force applied by an actuator in a physical system.
Having $b = 0$ as a limit point of $\cB$ means the system can become arbitrarily close to uncontrollable.
A more relevant multi-dynamics problem is variations
in mass or actuator strength,
whose signs are fixed.
In the scalar case, this could be modeled by
$a \geq \epsilon,\ b \geq \delta$ for some small $\epsilon, \delta > 0$.
These conditions ensure that the system requires nonzero control inputs for finite cost,
but the controller can be continuous. %
We extend this idea to multiple dimensions with the following definition.
\begin{definition}[Decomposed dynamics form]%
\label{def:B-SVD}
	Fix $A \in \R^{n \times n}$
	and a \emph{breadth} parameter $\breadth \geq 1$.
	Let
		$\Bset = \{ U \Sigma V^\top : \Sigma \in \bSigma \}$,
		where
		$\bSigma = \{ \diag(\sigma) : \sigma \in [\recip \breadth, 1]^d \}$.
	The matrices $U \in \R^{n \times d}$
	and
	$V \in \R^{m \times d}$ each have rank $d$, where
	$0 < d \leq \min \{n, m\}$.
	The tuple $(A, U, V, \breadth)$
	fully defines a \emph{\multienv\ LQR problem in decomposed dynamics form},
	or \emph{\DDFproblem} for brevity.
\end{definition}

A reduction to the form of
\citet{thorp-matchingconditions}
establishes that any \DDFproblem\
admits a robust controller
$K_{\mathrm{robust}}$,
meaning that $J_B(K_{\mathrm{robust}}) < \infty$
for all $B \in \cB$.
The continuity of the LQR cost \eqref{eq:cost-suboptimal} in $B$
and the compactness of $\Envs$ for any $\breadth$ imply that
$\coveringnum{\alpha}{\Envs_\breadth}$ is always finite.
Variations in $A$ are redundant in the scalar case where we focus our theoretical work in this paper.
The definition can be extended to include them in future work.




\paragraph{Linearized quadrotor example}
\input{decomposed_dynamics_examples.tex}
